Regression

### 2018-01-25 paper/R/paper.Rmd
jsd

library(igraph)
library(ggpmisc)
library(ggiraph)
library(RColorBrewer) 
library(ggrepel)
library(scales)      # Scales
library(viridis)     # Viridis color scales

@@

library(htmlwidgets) # JS visuliaztions
library(htmltools)   # Arbitrary html

@@

theme_set(
  theme_bw(base_family = "Roboto", base_size = 8) +
    theme(
      plot.title = element_text(size = 10,
                                margin = margin(0, 0, 4, 0, "pt")),
      plot.subtitle = element_text(size = 12),
      plot.caption = element_text(size = 6),
      panel.border = element_blank()
    )
)

rm(list=ls())
col <- brewer.pal(6,"Dark2")
```

@@

# reach <- reach %>% 
#   mutate(date = as.Date(Date, "%m/%d/%Y")) %>%
#   select(- c(Metric,Date)) %>%
#   gather(key="site", value="reach", focus.de:n.tv.de) %>%
#  filter(!site %in% drop) %>%
#   mutate(site = ifelse(site=="bild.de","Bild.de",site),
#        site = ifelse(site=="focus.de","FOCUS ONLINE",site),
#        site = ifelse(site=="spiegel.de","SPIEGEL ONLINE",site),
#        site = ifelse(site=="zeit.de","ZEIT ONLINE",site),
#        site = ifelse(site=="tagesschau.de","Tagesschau.de",site),
#        site = ifelse(site=="zdf.de","ZDF.de",site),
#        site = ifelse(site=="welt.de","DIE WELT",site),
#        site = ifelse(site=="n-tv.de","n-tv.de",site))

@@

```{r}
p1 <- views %>%
  filter(date > as.POSIXct("2017-05-31")) %>%
  ggplot(aes(date, views, color=site)) +
  geom_line(show.legend = F) +
  geom_text_repel(data = views[views$date==max(views$date), ],
                  aes(date, views, label=site),
                  size=2.8, show.legend = F, seed = 5) +
  scale_x_date(limits = c(as.Date("2017-05-31"),as.Date("2018-02-15")),
               breaks = date_breaks("1 month"), 
               labels=date_format("%B %y", tz="CET")) +
  theme(
      #legend.position   = "none",
      legend.text       =  element_text(size=6),
      plot.background   = element_rect("#fafafa", "#fafafa"),
      panel.background  = element_rect("#fafafa"),
      axis.title.x      = element_blank(),
      axis.text.y       = element_text(size = 8)
    ) +
  labs(x="", y="pageviews", color="", title = "", 
      caption = "Source: Alexa Internet, Inc. (www.alexa.com)" )

@@

p1 <- views %>% 
  filter(date >= as.Date("2017-09-17") &
                   date <= as.Date("2017-10-01")) %>%
  ggplot(aes(date, perc_change, color=factor(site))) +
  geom_line(show.legend = F) +
  geom_text_repel(data = views[views$date=="2017-09-24", ],
                  aes(date, perc_change, label=site),
                  size=2.8, show.legend = F, seed = 5) +
  #scale_color_manual(values = brewer.pal(8,"Dark2")) +
  scale_x_date(breaks = date_breaks("1 day"), labels=date_format("%d.%m.", tz="CET")) +
  labs(x="",y="% change", color="") +
  theme(
      legend.text       =  element_text(size=6),
      plot.background   = element_rect("#fafafa", "#fafafa"),
      panel.background  = element_rect("#fafafa"),
      axis.title.x      = element_blank(),
      axis.text.y       = element_text(size = 8)
    )

@@

source <- left_join(source1, source2,
                    by=c("Date","Metric")) %>%
  select(- c(Date)) %>%
  gather(key="site", value="traffic", 
         focus.de:tagesspiegel.de)
```

```{r}
p1 <- ggplot(source, aes(site, traffic, fill=Metric,
                   label = round(traffic, digits = 2))) +
  geom_col(alpha = 0.8) +
  geom_text(size = 2, position = position_stack(vjust = 0.5)) +
  labs(x = "", y = "Percentage of total traffic", 
       caption = "Source: Alexa Internet, Inc. (www.alexa.com)") +
  theme(axis.text.x = element_text(angle = 45, size = 7 ))

@@

```{r}
keepsite <- c("tagesschau.de", "spiegel.de", "zeit.de", "deutschlandfunk.de",
              "zdf.de", "bild.de", "welt.de", "stern.de", "sueddeutsche.de", "focus.de")

keywords.df <- keywords.df %>% 
  filter(nchar(as.character(site))>1)
#  filter(site %in% keepsite)

unique(keywords.df$site)
```

### Search Traffic %
```{r}
p1 <- keywords.df %>%
  arrange(desc(Percent_of_traffic)) %>%
  group_by(site) %>%
  top_n(10, Percent_of_traffic) %>%
  ungroup() %>%
  ggplot(aes(reorder(term, Percent_of_traffic), 
             Percent_of_traffic, fill=site)) +
  geom_col(show.legend = FALSE) +
  theme_bw(base_family = "Roboto", base_size = 4) +
  coord_flip() +
  facet_wrap(~site, scales = "free") +
  labs(x= "", y = "Search traffic %", 
       title = "",
       caption = "Source: Alexa Internet, Inc. (www.alexa.com)")

@@

ggsave(plot= p1,
filename = "../figs/search_traffic.png", device = "png",
width = 7, height = 4,
        dpi = 600
)
```

@@

```{r}
p1 <- keywords.df %>%
  filter(term %in% keyword1) %>%
  ggplot(aes(site,
             Share_of_voice, fill=term)) +
  geom_col(show.legend = F) +
  coord_flip() +
  facet_grid(~term, scales = "free") +
  labs(x= "", y = "Share of voice",
       title = ""
       )

@@

```{r}
p1 <- keywords.df %>%
  filter(term %in% keyword2) %>%
  ggplot(aes(site,
             Share_of_voice, fill=term)) +
  geom_col(show.legend = F) +
  coord_flip() +
  facet_grid(~term) +
  labs(x= "", y = "Share of voice",
       caption = "
  Source: Alexa Internet, Inc. (www.alexa.com)
      ",
       title = ""
       )

@@

## Audience Network
```{r}
focus <- read.csv("../data/audience_network/Audience_Overlap_1_15_2018_focus.csv", header=FALSE, comment.char="#")
spiegel <- read.csv("../data/audience_network/Audience_Overlap_1_15_2018_spiegel.csv", header=FALSE, comment.char="#")
bild <- read.csv("../data/audience_network/Audience_Overlap_1_15_2018_bildde.csv", header=FALSE, comment.char="#")
zeit <- read.csv("../data/audience_network/Audience_Overlap_1_15_2018_zeitde.csv", header=FALSE, comment.char="#")
tagesschau <- read.csv("../data/audience_network/Audience_Overlap_1_15_2018_tagesschau.csv", header=FALSE, comment.char="#")

zdf <-  read.csv("../data/audience_network/Audience_Overlap_1_15_2018_zdf.csv.crdownload.csv", header=FALSE, comment.char="#")
#stern <- read.csv("../data/audience_network/Audience_Overlap_1_15_2018_stern.csv", header=FALSE, comment.char="#")
welt <- read.csv("../data/audience_network/Audience_Overlap_1_15_2018 _welt.csv", header=FALSE, comment.char="#")
```

```{r}
focus <- focus[-1,1:2] 
colnames(focus) <- c("site","focus.de")

spiegel <- spiegel[-1,1:2] 
colnames(spiegel) <- c("site","spiegel.de")

bild <- bild[-1,1:2] 
colnames(bild) <- c("site","bild.de")

zeit <- zeit[-1,1:2] 
colnames(zeit) <- c("site","zeit.de")

tagesschau <- tagesschau[-1,1:2] 
colnames(tagesschau) <- c("site","tagesschau.de")

zdf <- zdf[-1,1:2] 
colnames(zdf) <- c("site","zdf.de")

welt <- welt[-1,1:2] 
colnames(welt) <- c("site","welt.de")
```

```{r}
# combine dataframes
network_df <- left_join(focus[1:80,], spiegel[1:80,], by="site") %>%
  left_join(., bild[1:80,], by = "site") %>%
  left_join(., zeit[1:80,], by = "site") %>%
  left_join(., tagesschau[1:80,], by = "site") %>%
  left_join(., zdf[1:80,], by = "site") %>%
  left_join(., welt[1:80,], by = "site")

network_df <- na.omit(network_df)

melted <- network_df %>%
    gather(key="seed", value="score", focus.de:welt.de) %>%
  mutate(score = as.integer(score),
         site = as.factor(site),
         seed = as.factor(seed))
```

```{r}
p1 <- ggplot(melted, aes(seed, site, fill=score)) +
  geom_tile() +
  scale_fill_gradient(low="gray95",high=col[3]) +
  scale_x_discrete(labels=c("bilde.de" = "Bild.de", 
                            "focus.de" = "FOCUS ONLINE", 
                            "spiegel.de" = "SPIEGEL ONLINE",
                            "tagesschau.de" = "Tagesschau.de", 
                            "welt.de" ="DIE WELT",
                            "zdf.de" = "ZDF.de",
                            "zeit.de" = "ZEIT ONLINE")) +
  labs(x="", y="",  caption = "
  Source: Alexa Internet, Inc. (www.alexa.com)
      ") +
  theme(
      legend.text       =  element_text(size=6),
      plot.background   = element_rect("#fafafa", "#fafafa"),
      panel.background  = element_rect("#fafafa"),
      axis.title.x      = element_blank(),
      axis.text.x = element_text(size=8, angle = 45),
      axis.text.y       = element_text(size = 8)
    )

ggsave(plot= p1,
filename = "../figs/audience.png", device = "png",
width = 5, height = 6,
        dpi = 600
)

p1
```

@@

## Distribution of articles
```{r message=FALSE, warning=FALSE}
ggsave({
  btw %>%
  ggplot(aes(site)) +
  geom_bar(fill=col, alpha= .8) +
  labs(x="", y="Number of articles") +
  theme(
      legend.position   = "none",
      plot.background   = element_rect("#fafafa", "#fafafa"),
      plot.title        = element_text(size = 18),
      plot.subtitle     = element_text(size = 8),
      plot.caption      = element_text(size = 7),
      panel.background  = element_rect("#fafafa"),
      axis.title.x      = element_blank(),
      axis.text.y       = element_text(size = 8)
    )

@@

```{r message=FALSE, warning=FALSE}
ggsave({
  btw %>%
  group_by(date, site) %>%
  dplyr::summarise(obs = n()) %>%
  ggplot(aes(date, obs, color = site)) +
  geom_line() +
  #geom_vline(aes(xintercept=as.Date("2017-09-24")),
  #           linetype = 2, color="grey40") +
  #geom_vline(aes(xintercept=as.Date("2017-11-20")),
  #               linetype = 2, color="grey40") +
  scale_color_manual(values = col) +
  labs(x="", y="Count",color="") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(
      #legend.position   = "none",
      plot.background   = element_rect("#fafafa", "#fafafa"),
      plot.title        = element_text(size = 18),
      plot.subtitle     = element_text(size = 8),
      plot.caption      = element_text(size = 7),
      #panel.grid        = element_blank(),
      panel.background  = element_rect("#fafafa"),
      axis.title.x      = element_blank(),
      axis.text.y       = element_text(size = 8)
    )
},
filename = "../figs/timeline.png", device = "png",width = 7, height = 4,
dpi = 600
)

@@

## Label topics
```{r}
sagelabs <- sageLabels(stmOut, 100)
```

@@

After reviewing a sample of articles assigned to the respective topic, we assign a shorter name to the topics based on the most common words in order to improve readability and traceability.
```{r}
sagelabs$cov.betas[[1]]$problabels[,1:10]
```

```{r}
topics <- matrix(c(1, "Great coalition", 2, "Merkel,election campaign", 3, "Jamaica coalition", 
                   4, "Diesel scandal", 5, "Merkel chancellor", 6, "Seehover vs. Söder", 
                   7, "Germany, EU, Jamaika", 8, "Merkel vs.Schulz", 9, "AfD election results", 
                   10, "Steinmeier,Federal President", 11, "unclear (Schröder, Google)", 
                   12, "Federal Election in social media", 13, "Climate policy", 14, "G20 Hamburg", 
                   15, "error", 16, "Education, Pension policy", 17, "Reports on individuals",
                   18, "Family reunion refugees", 19, "Polls federal election", 
                   20, "AfD top candidates Weidel, Storch", 21, "M.Schwesig (SPD)",
                   22, "elections in Niedersachsen", 23, "Böhmermann vs. Erdogan", 
                   24, "political talkshows", 25, "German armed forces", 26, "W.Schäuble", 
                   27, "C.Lindner FDP", 28, "Turkey, Russia", 29, "A.Merkel Youtube", 
                   30, "H.Kohl obituary", 31, "AfD Gauland, Höcke", 32, "Asylum claims and deportation", 
                   33, "EU policies", 34, "DIE LINKE", 35, "SPD", 36, "Islam and antisemitism in GER", 
                   37, "AfD in parliament", 38, "Terror attacks (GER)  & police reports", 
                   39, "Church", 40, "RAF"), ncol=2, byrow=T)
```

@@

topics.df <- as.data.frame(topics) %>% transmute(topic = as.integer(V1),
                                 topic_name = paste(topic, V2, sep=": "))

@@

p1 <- ggplot(frequency, aes(x=reorder(topic, frequency), y=frequency)) + 
    geom_col(fill=col[1], alpha=0.8) +
    coord_flip() +
    labs(x="", y="expected frequency") +
    theme(axis.text = element_text(size=8),
          axis.title = element_text(size=10))

@@

#ggsave(plot = p1, filename = "../figs/topic_proportion.png", device = "png",width = 8, height = 12,
#dpi = 600)
```

## by newspaper
```{r}
plotNewspaperHistogram <- function(topic){
  tab <- tapply(stmOut$theta[,topic], stmOut$settings$covariates$betaindex, mean)
  tab <- as.data.frame(tab) %>% 
    mutate(site=stmOut$settings$covariates$yvarlevels)

@@

## Topic Correlation
```{r}
topicCorrelation <- function(ylevel) {
  cormat <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==ylevel,])
  adjmat <- ifelse(cormat > .04,1,0)

  corr <- list()
  corr$posadj <- adjmat
  corr$poscor <- cormat*adjmat
  corr$cor <- ifelse(abs(cormat)>.04,cormat,0)

  x <- corr$posadj[1:nrow(corr$posadj),1:nrow(corr$posadj)]

  g<- graph.adjacency(x, mode="undirected", weighted=TRUE, diag=FALSE)

  E(g)$size <- 1
  E(g)$lty <- 2
  E(g)$color <- "black"
  V(g)$label <- topics[,2]
  layout <- layout_nicely

  plot.igraph(g, layout=layout_nicely, vertex.color="white", label.font = "Roboto",
     vertex.frame.color="grey", vertex.size=1, vertex.label.cex=.6, edge.color="red",
     edge.width=1, main=paste("Topic correlation", stmOut$settings$covariates$yvarlevels[ylevel]))
}
```

```{r}
topicCorrelation(5)
```

### Overlapping Correlation
```{r}
topicCorrCompare <- function(ylevel1, ylevel2) {

  # find all edges between topics where they exhibit a positive correlation above 0.1
  cormat <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==ylevel1,])
  adjmat <- ifelse(cormat > .1,1,0)

  corr.1 <- list()
  corr.1$posadj <- adjmat
  corr.1$poscor <- cormat*adjmat
  corr.1$cor <- ifelse(abs(cormat)>.04,cormat,0)

  # Ylevel 2
  cormat <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==ylevel2,])
  adjmat <- ifelse(cormat > .1,1,0)

  corr.2 <- list()
  corr.2$posadj <- adjmat
  corr.2$poscor <- cormat*adjmat
  corr.2$cor <- ifelse(abs(cormat)>.04,cormat,0)

  # Prepare plot
  g.1 <- graph.adjacency(corr.1$cor, mode="undirected", weighted = T, diag = F) 
  g.2 <- graph.adjacency(corr.2$cor, mode = "undirected", weighted = T, diag = F)

  inter.graph <- graph.intersection(g.1, g.2)
  added.subgraph <- graph.difference(g.1, inter.graph)
  subs.subgraph <- graph.difference(g.2, inter.graph)

  # Styling
  E(added.subgraph)$color <- col[1]
  E(subs.subgraph)$color <- col[2]
  E(inter.graph)$color <- col[3]

  # Matrix
  g.whole<-graph.union(inter.graph,added.subgraph,subs.subgraph)
  V(g.whole)$color<-col[3]
  E(g.whole)$color <- col[2]
  E(g.whole)[1:length(E(inter.graph))]$color<-col[3]
  E(g.whole)[(length(E(inter.graph))+1):(length(E(inter.graph))+length(E(added.subgraph)))]$color<-col[1]

  inter.list <- get.edgelist(inter.graph)
  list.1 <- get.edgelist(added.subgraph)
  list.2 <- get.edgelist(subs.subgraph)

  # Set Frame
  cormat <- matrix(0, nrow=100, ncol=100)
  for(i in 1:nrow(inter.list)){
    cormat[inter.list[i,1], inter.list[i,2]] <- .5
    cormat[inter.list[i,2], inter.list[i,1]] <- .5
    }

  for(i in 1:nrow(list.1)){
    cormat[list.1[i,1], list.1[i,2]] <- -1
    cormat[list.1[i,2], list.1[i,1]] <- -1
    }

  for(i in 1:nrow(list.2)){
    cormat[list.2[i,1], list.2[i,2]] <- 1
    cormat[list.2[i,2], list.2[i,1]] <- 1
    }

  cormat <- cormat[as.numeric(topics[,1]),as.numeric(topics[,1])]
  topics2 <- sapply(topics[,2], function (x) str_replace(x, "\n", ""))
  rownames(cormat) <- colnames(cormat) <- topics.df$topic_name

  only.1 <- apply(cormat,1, function (x) sum(x==1))
  only.2 <- apply(cormat,1, function (x) sum(x==-1))
  both <- apply(cormat,1, function (x) sum(x==.5))
  all <- apply(cormat,1, function (x) sum(x!=0))
  disagree <- only.1/all + only.2/all

  disagreed <- order(disagree, decreasing=F)
  list <- topics[disagreed,2]
  disagreemat <- cormat[disagreed, disagreed]
  rownames(disagreemat) <- topics2[disagreed]
  colnames(disagreemat) <- topics2[disagreed]

  corrplot(disagreemat, cl.pos="n", tl.col="black", tl.cex=.5)
  legend(40,20, c(paste(stmOut$settings$covariates$yvarlevels[ylevel1]), paste(stmOut$settings$covariates$yvarlevels[ylevel2]), "Both", "None"),
         col=c("darkred", "darkblue", "lightblue", "white"), 
         pch=c(15,15,16,16), cex = 0.7, box.lty = 0)
}
```

Pairs of topics where an edge exists in both Newspaper, we denote with a light blue dot. Pairs of topics where Newspaper1, but not Newspaper2 have an edge between them, we denote with a red square, and those where Newspaper2, but not Newspaper1 have an edge between them we denote with a blue square.
We then sort the matrix by topics that are similarly correlated with other topics in Newspaper1 and Newspaper2 to those that are not similarly correlated.
```{r}
topicCorrCompare(3,5)
```

## How they talk about GroKo differently

>>>>

library(igraph)
library(corrplot)
library(ggpmisc)
library(ggiraph)
library(RColorBrewer) 
library(ggrepel)
library(scales)      # Scales
library(viridis)     # Viridis color scales

@@

@@

theme_set(
  theme_bw(base_family = "Roboto", base_size = 8) +
    theme(
      plot.title = element_text(size = 10,
                                margin = margin(0, 0, 4, 0, "pt")),
      plot.subtitle = element_text(size = 12),
      plot.caption = element_text(size = 6),
      plot.background   = element_rect("#fafafa", "#fafafa"),
      panel.background  = element_rect("#fafafa"),
      panel.border = element_blank()
    )
)

rm(list=ls())
col <- brewer.pal(6,"Dark2")
source("func/functions.R")
```

@@

# reach <- reach %>%
#   mutate(date = as.Date(Date, "%m/%d/%Y")) %>%
#   select(- c(Metric,Date)) %>%
#   gather(key="site", value="reach", focus.de:n.tv.de) %>%
#  filter(!site %in% drop)

views <- views %>%
  mutate(site = ifelse(site=="bild.de","Bild.de",site),
       site = ifelse(site=="focus.de","FOCUS ONLINE",site),
       site = ifelse(site=="spiegel.de","SPIEGEL ONLINE",site),
       site = ifelse(site=="zeit.de","ZEIT ONLINE",site),
       site = ifelse(site=="tagesschau.de","Tagesschau.de",site),
       site = ifelse(site=="zdf.de","ZDF.de",site),
       site = ifelse(site=="welt.de","DIE WELT",site),
       site = ifelse(site=="n-tv.de","n-tv.de",site))

@@

```{r}
p1 <- views %>%
  filter(date > as.POSIXct("2017-05-31")) %>%
  ggplot(aes(date, views, color=site)) +
  geom_line(show.legend = F) +
  geom_text_repel(data = views[views$date==max(views$date), ],
                  aes(date, views, label=site),
                  size=2.8, show.legend = F, seed = 1) +
  scale_x_date(limits = c(as.Date("2017-05-31"),as.Date("2018-02-15")),
               breaks = date_breaks("1 month"), 
               labels=date_format("%B %y", tz="CET")) +
  theme(
      #legend.position   = "none",
      legend.text       =  element_text(size=6),
      axis.text.y       = element_text(size = 8)
    ) +
  labs(x="", y="pageviews", color="", title = "", 
      caption = "Source: Alexa Internet, Inc. (www.alexa.com)" )

@@

p1 <- views %>% 
  filter(date >= as.Date("2017-09-17") &
                   date <= as.Date("2017-10-01")) %>%
  ggplot(aes(date, perc_change, color=factor(site))) +
  geom_line(show.legend = F) +
  geom_text_repel(data = views[views$date=="2017-09-24", ],
                  aes(date, perc_change, label=site),
                  size=3, show.legend = F, seed = 5) +
  #scale_color_manual(values = brewer.pal(8,"Dark2")) +
  scale_x_date(breaks = date_breaks("1 day"), labels=date_format("%d.%m.", tz="CET")) +
  labs(x="",y="% change", color="") +
  theme(
      legend.text       =  element_text(size=6),
      axis.text.y       = element_text(size = 8)
    )

@@

source <- left_join(source1, source2,
                    by=c("Date","Metric")) %>%
  select(- c(Date)) %>%
  gather(key="site", value="traffic", 
         focus.de:tagesspiegel.de)

source <- source %>%
  mutate(site = ifelse(site=="bild.de","Bild.de",site),
       site = ifelse(site=="focus.de","FOCUS ONLINE",site),
       site = ifelse(site=="spiegel.de","SPIEGEL ONLINE",site),
       site = ifelse(site=="zeit.de","ZEIT ONLINE",site),
       site = ifelse(site=="tagesschau.de","Tagesschau.de",site),
       site = ifelse(site=="zdf.de","ZDF.de",site),
       site = ifelse(site=="welt.de","DIE WELT",site),
       site = ifelse(site=="n-tv.de","n-tv.de",site))

```{r}
p1 <- ggplot(source, aes(site, traffic, fill=Metric,
                   label = round(traffic, digits = 2))) +
  geom_col(alpha = 0.8) +
  geom_text(size = 2, position = position_stack(vjust = 0.5)) +
  labs(x = "", y = "Percentage of total traffic", 
       caption = "Source: Alexa Internet, Inc. (www.alexa.com)") +
  theme(axis.text.x = element_text(angle = 45, size = 8 ))

@@

```{r}
keepsite <- c("tagesschau.de", "spiegel.de", "zeit.de", 
              "bild.de", "welt.de", "focus.de")

keywords.df.reduced <- keywords.df %>% 
  filter(nchar(as.character(site))>1) %>% filter(site %in% keepsite)
```

```{r}
keywords.df <- keywords.df %>%
  mutate(site = as.character(site)) %>%
  mutate(site = ifelse(site=="bild.de","Bild.de",site),
       site = ifelse(site=="focus.de","FOCUS ONLINE",site),
       site = ifelse(site=="spiegel.de","SPIEGEL ONLINE",site),
       site = ifelse(site=="zeit.de","ZEIT ONLINE",site),
       site = ifelse(site=="tagesschau.de","Tagesschau.de",site),
       site = ifelse(site=="deutschlandfunk.de","DLF",site),
       site = ifelse(site=="zdf.de","ZDF.de",site),
       site = ifelse(site=="welt.de","DIE WELT",site),
       site = ifelse(site=="n-tv.de","n-tv.de",site))
```

### Search Traffic %
```{r}
p1 <- keywords.df %>%
  arrange(desc(Percent_of_traffic)) %>%
  group_by(site) %>%
  top_n(10, Percent_of_traffic) %>%
  ungroup() %>%
  ggplot(aes(reorder(term, Percent_of_traffic), 
             Percent_of_traffic, fill=site)) +
  geom_col(fill=col[1], show.legend = FALSE) +
  theme_bw(base_family = "Roboto", base_size = 7) +
  coord_flip() +
  facet_wrap(~site, scales = "free") +
  labs(x= "", y = "Search traffic %", 
       title = "",
       caption = "Source: Alexa Internet, Inc. (www.alexa.com)")

@@

ggsave(plot= p1,
filename = "../figs/search_traffic.png", device = "png",
width = 9, height = 5,
        dpi = 600
)
```

@@

```{r}
p1 <- keywords.df %>%
  filter(term %in% keyword1) %>%
  ggplot(aes(site,
             Share_of_voice, fill=term)) +
  geom_col(fill=col[3], show.legend = F) +
  coord_flip() +
  facet_grid(~term, scales = "free") +
  labs(x= "", y = "Share of voice",
       title = ""
       )

@@

```{r}
p1 <- keywords.df %>%
  filter(term %in% keyword2) %>%
  ggplot(aes(site,
             Share_of_voice, fill=term)) +
  geom_col(fill=col[3], show.legend = F) +
  coord_flip() +
  facet_grid(~term) +
  labs(x= "", y = "Share of voice",
       caption = "
  Source: Alexa Internet, Inc. (www.alexa.com)
      ",
       title = ""
       )

@@

@@

## Distribution of articles
```{r message=FALSE, warning=FALSE}
ggsave({
  btw %>%
  ggplot(aes(site)) +
  geom_bar(fill=col[1], alpha= .8) +
  labs(x="", y="Number of articles") +
  theme(
      legend.position   = "none"
    )

@@

```{r message=FALSE, warning=FALSE}
ggsave({
  btw %>%
  group_by(date) %>%
  dplyr::summarise(obs = n()) %>%
  ggplot(aes(date, obs)) +
  geom_line(color=col[3]) +
  geom_vline(aes(xintercept=as.Date("2017-09-24")),
             linetype = 2, color=col[2]) +
  scale_color_manual(values = col) +
  labs(x="", y="number of articles",color="") +
  scale_x_date(breaks = date_breaks("1 month"), labels=date_format("%B", tz="CET")) +
  theme(
      legend.position   = "none",
      axis.title.x      = element_blank(),
      axis.text       = element_text(size = 8)
    )
},
filename = "../figs/timeline.png", device = "png",width = 7, height = 4,
dpi = 600
)

@@

## Label topics
```{r}
sagelabs <- sageLabels(stmOut, 25)
```

@@

After reviewing a sample of articles assigned to the respective topic, we assign a shorter name to the topics based on the most common words in order to improve readability and traceability.
```{r}
sagelabs$cov.betas[[5]]$problabels[,1:10]
```

```{r}
topics <- matrix(c(1, "Great coalition", 2, "Merkel vs. CSU", 3, "Jamaica coalition", 
                   4, "Diesel scandal", 5, "Merkel as chancellor", 6, "Seehover vs. Söder", 
                   7, "political trends after the election", 8, "Merkel vs.Schulz", 9, "AfD election results", 
                   10, "Steinmeier,Federal President", 11, "IT themes (Data policy, Wifi, Telekom)", 
                   12, "Federal Election in social media", 13, "Climate policy", 14, "G20 Hamburg", 
                   15, "error (text processing failure)", 16, "Education, Pension policy",
                   17, "Reports on individuals", 18, "Family reunion refugees", 19, "Polls federal election", 
                   20, "AfD top candidates Weidel, Storch", 21, "M.Schwesig (SPD)",
                   22, "elections in Niedersachsen", 23, "Court sentences (NSU, Böhmermann vs. Erdogan)", 
                   24, "election capaigns & political talkshows", 25, "German armed forces", 26, "W.Schäuble", 
                   27, "C.Lindner FDP", 28, "Turkey, Russia", 29, "railway problems (DBahn)", 
                   30, "H.Kohl obituary", 31, "AfD Gauland, Höcke", 32, "Asylum claims and deportation", 
                   33, "EU policies", 34, "DIE LINKE", 35, "SPD", 36, "Islam and antisemitism in GER", 
                   37, "AfD in parliament", 38, "Terror attacks (GER)  & police reports", 
                   39, "Church", 40, "RAF"), ncol=2, byrow=T)

topics.df <- as.data.frame(topics) %>%
  transmute(topic_name = paste(V1, V2, sep=": "),
         topic = 1:40) 
```

@@

@@

p1 <- ggplot(frequency, aes(x=reorder(topic, frequency), y=frequency)) + 
    geom_col(fill=col[1], alpha=0.8) +
    coord_flip() +
    labs(x="", y="expected frequency") +
    theme(axis.text.x = element_text(size=8),
          axis.text.y = element_text(size=11),
          axis.title = element_text(size=10))

@@

ggsave(plot = p1, filename = "../figs/topic_proportion.png", device = "png",width = 8, height = 12,
dpi = 600)
```

### by newspaper
```{r}
plotNewspaperHistogram <- function(topic){
  tab <- tapply(stmOut$theta[,topic], stmOut$settings$covariates$betaindex, mean)
  tab <- as.data.frame(tab) %>% 
    mutate(site=stmOut$settings$covariates$yvarlevels)

@@

### Difference in topic prevalence
The estimateEffect() function explores how prevalence of topics varies across documents according to document covariates (metadata). First, users must specify the variable that they wish to use for calculating an effect. If there are multiple variables specified in estimateEffect(), then all other variables are held at their sample median. These parameters include the expected proportion of a document that belongs to a topic as a function of a covariate, or a first difference type estimate, where topic prevalence for a particular topic is contrasted for two groups.

```{r}
effect <- estimateEffect(c(1:40) ~site+s(month), stmOut, 
                         metadata = out$meta, uncertainty = "None")
#plot.estimateEffect(effect, "month", topics=c(33), method = "continuous", npoints=500)
```

```{r}
summary(effect)
```

```{r}
tables <- vector(mode="list", length = length(effect$topics))

for (i in seq_along(effect$topics)) {
  sims <- lapply(effect$parameters[[i]], function(x) stm:::rmvnorm(500, x$est, x$vcov))
  sims <- do.call(rbind, sims)
  est <- colMeans(sims)
  se <- sqrt(apply(sims,2, stats::var))
  tval <- est/se
  rdf <- nrow(effect$data) - length(est)
  p <- 2*stats::pt(abs(tval), rdf, lower.tail = FALSE)
  topic <- i

  coefficients <- cbind(topic, est, se, tval, p)
  rownames(coefficients) <- attr(effect$parameters[[1]][[1]]$est, "names") 
  colnames(coefficients) <- c("topic", "Estimate", "Std. Error", "t value", "p")
  tables[[i]] <- coefficients
}

out <- list(call=effect$call, topics=effect$topics, tables=tables)
```

```{r}
coeff <- as.data.frame(do.call(rbind,out$tables))

coeff <- coeff %>% 
  mutate(parameter = rownames(coeff),
         parameter = gsub("site", "", parameter),
         parameter = ifelse(parameter == "s(month)1", "1_July", parameter),
         parameter = ifelse(parameter == "s(month)2", "2_August", parameter),
         parameter = ifelse(parameter == "s(month)3", "3_September", parameter),
         parameter = ifelse(parameter == "s(month)4", "4_October", parameter),
         parameter = ifelse(parameter == "s(month)5", "5_November", parameter),
         parameter = ifelse(parameter == "s(month)6", "6_December", parameter),
         signifcant = ifelse(p <= 0.5,"yes","no")) %>%
  left_join(., topics.df, by="topic")
```

```{r}
sites <- c("(Intercept)", "DIE WELT", "FOCUS ONLINE","SPIEGEL ONLINE", "Tagesschau.de","ZEIT ONLINE")

p1 <- coeff %>% filter(parameter %in% sites) %>%
  ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, fill=factor(signifcant))) +
  geom_col() +
  scale_fill_manual(values = col[c(2,1)]) +
  coord_flip() +
  facet_wrap(~parameter, ncol = 6) +
  labs(x="", fill="significant at\nthe 5% level") +
  theme(axis.text.x = element_text(angle=90))

ggsave(plot = p1, filename = "../figs/estimates_site.png", device = "png",width = 9, height = 5,
dpi = 600)
```

```{r}
p1 <- coeff %>% filter(!parameter %in% sites) %>%
  ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, 
             fill=factor(signifcant))) +
  geom_col() +
  scale_fill_manual(values = col[c(2,1)]) +
  coord_flip() +
  facet_wrap(~parameter, ncol = 6) +
  labs(x="", fill="significant at\nthe 5% level") +
  theme(axis.text.x = element_text(angle=90))

ggsave(plot = p1, filename = "../figs/estimates_month.png", device = "png",width = 9, height = 5,
dpi = 600)
```

## Topic Correlation
```{r}
## Create Dataframe with correlations

cor <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==1,])
colnames(cor) <- 1:40

df <- as.data.frame(cor) %>% 
  mutate(topic = 1:40) %>%
  melt(., id="topic", value.name="corr") %>%
  mutate(site = stmOut$settings$covariates$yvarlevels[1])

for (i in 2:6) {
  cor <- cor(stmOut$theta[stmOut$settings$covariates$betaindex==i,])
  colnames(cor) <- 1:40

  df1 <- as.data.frame(cor) %>% 
    mutate(topic = 1:40) %>%
    melt(., id="topic", value.name="corr") %>%
    mutate(site = stmOut$settings$covariates$yvarlevels[i])

  df <- rbind(df,df1)
}
```

```{r}
df <- df %>% 
  left_join(.,topics.df, by = "topic") %>%
  mutate(topic1 = topic,
         topic_name1 = topic_name,
         topic = as.numeric(variable)) %>%
  select(-topic_name) %>%
  left_join(., topics.df, by="topic")
```

```{r}
p1 <- df %>%
  filter(corr>0.1 & corr < 1) %>%
  ggplot(aes(reorder(topic_name1,topic1), topic_name, 
             fill=corr)) +
  geom_tile() +
  facet_wrap(~site, ncol = 6) +
  scale_fill_distiller(palette = "Spectral", trans = "reverse") + 
  labs(x="", y="", fill="correlation") +
  theme_bw(base_family = "Roboto", base_size = 10) +
  theme(axis.text.x = element_text(angle=90, size = 6),
        #plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
        axis.ticks = element_line(colour = 'transparent'))

ggsave(plot = p1, filename = "../figs/topic_correlation.png", device = "png",width = 9, height = 5,
dpi = 600)
```

### Overlapping Correlation
Pairs of topics where an edge exists in both Newspaper, we denote with a light blue dot. Pairs of topics where Newspaper1, but not Newspaper2 have an edge between them, we denote with a red square, and those where Newspaper2, but not Newspaper1 have an edge between them we denote with a blue square.
We then sort the matrix by topics that are similarly correlated with other topics in Newspaper1 and Newspaper2 to those that are not similarly correlated.
```{r}
png("../figs/overlapping_correlation.png")
topicCorrCompare(1,5)
dev.off()
```

### Distance metric
